Analysis

### 2022-12-08 analysis/analysis.Rmd
post revision fix neotoma data retrieval

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!webshot::is_phantomjs_installed()) webshot::install_phantomjs()
library(magick)
```

@@

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(mapview)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
```

@@

```{r message=FALSE}
if(!require('devtools')) install.packages('devtools')
library(devtools)
install_github('ISAAKiel/aoristAAR')
require(aoristAAR)
```

@@

```{r message=FALSE, warning=FALSE}
pollen_data <- get_download(pollen_locations$neotoma_id)
```

@@

```{r}
pollen_data_filtered <- filter_by_unit(filter_by_element(pollen_data, "pollen"), "NISP")
class(pollen_data_filtered) <- append(class(pollen_data_filtered), "download_list")
```

@@

```{r}
pollen_data_comp <- transform_to_percent(pollen_data_filtered)
```

@@

```{r}
all_output <- suppressWarnings(neotoma::compile_downloads(pollen_data_comp))
```

@@

```{r}
timeframe <- c(-7000,-1000)
all_output <- subset(all_output, 1950-age > timeframe[1] & 1950-age < timeframe[2])
```

@@

```{r}
all_data <- all_output[,11:ncol(all_output)]
all_data[is.na(all_data)] <- 0
```

@@

```{r}
orientation <- sign(scores(res.pca)$species["Cerealia",1])
res.open <- data.frame(scores(res.pca, choices = 1, display = "si")*orientation)
colnames(res.open) <- "score"
res.open$age <- all_output$age
res.open$site <- all_output$site.name
ggplot(res.open) + geom_line(aes(x = 1950-age, y = score, color = site))
```

@@

```{r}
all_proxies <- merge(res.sumcal, res.open_final, by.x = "calBP", by.y = "age") %>%
  merge(res.aorist, by.x = "calBP", by.y = "age") %>%
  merge(res.lss, by.x = "calBP", by.y = "age") %>%
  select(calBP, PrDens, mean, sum, moving_mean) %>%
  rename(age = calBP, sumcal = PrDens, openness = mean, aoristic_sum = sum, dendro = moving_mean) %>%
  filter(age < 8000 & age > 3000)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setenv(OPENSSL_CONF="/etc/ssl/")
if (!webshot::is_phantomjs_installed()) webshot::install_phantomjs()
library(magick)
```

@@

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(mapview)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
library(grid)
```

@@

```{r message=FALSE}
if(!require('devtools')) install.packages('devtools')
library(devtools)
install_github('ISAAKiel/aoristAAR')
require(aoristAAR)
```
Also, neotoma is not longer available on cran, and it has been replaced by neotoma2, so we had to replace it. That is why we have to load it again:

```{r}
if(!require('neotoma2')) devtools::install_github('NeotomaDB/neotoma2')
require(neotoma2)
```

@@

```{r message=FALSE, warning=FALSE}
pollen_data <- get_downloads(pollen_locations$neotoma_id, all_data=T)
```

@@

```{r}
pollen_data.samples <- samples(pollen_data)

pollen_data.samples.filtered <- pollen_data.samples %>% subset(element == "pollen" & units == "NISP")
```

@@

```{r}
pollen_data_comp <- transform_to_percent(pollen_data.samples.filtered)
```

@@

```{r}
all_output <- pollen_data_comp
```

@@

```{r}
timeframe <- c(-7000,-1000)
all_output <- subset(all_output, 1950-age > timeframe[1] & 1950-age < timeframe[2])
all_output[is.na(all_output)] <- 0
```

@@

```{r}
all_data <- all_output[, !(colnames(all_output) %in%  c("age", "sampleid", "sitename"))]
```

@@

```{r}
orientation <- sign(scores(res.pca)$species["Cerealia",1])
res.open <- data.frame(scores(res.pca, choices = 1, display = "si")*orientation)
colnames(res.open) <- "score"
res.open$age <- all_output$age
res.open$site <- all_output$sitename
ggplot(res.open) + geom_line(aes(x = 1950-age, y = score, color = site))
```

@@

```{r}
all_proxies <- merge(res.sumcal, res.open_final, by.x = "calBP", by.y = "age") %>%
  merge(res.aorist, by.x = "calBP", by.y = "age") %>%
  merge(res.lss, by.x = "calBP", by.y = "age") %>%
  select(calBP, PrDens, mean, sum, moving_mean) %>%
  rename(age = calBP, sumcal = PrDens, openness = mean, aoristic_sum = sum, dendro = moving_mean) %>%
  dplyr::filter(age < 8000 & age > 3000)
